\chapter{Experimental Design}\label{experimental-design}

Dyin' ain't much of a livin', boy. Two little mice fell in a bucket of
cream. The first mouse quickly gave up and drowned. The second mouse,
wouldn't quit. He struggled so hard that eventually he churned that
cream into butter and crawled out. Gentlemen, as of this moment, I am
that second mouse. I'm neglecting my other guests. Enjoy yourself,
you'll find the young ladies stimulating company. Ever notice how
sometimes you come across somebody you shouldn't have F**ked with? Well,
I'm that guy. This is the AK-47 assault rifle, the preferred weapon of
your enemy; and it makes a distinctive sound when fired at you, so
remember it. Two little mice fell in a bucket of cream. The first mouse
quickly gave up and drowned. The second mouse, wouldn't quit. He
struggled so hard that eventually he churned that cream into butter and
crawled out. Gentlemen, as of this moment, I am that second mouse. This
is America, babe, you gotta think big to be big. This is my gun, Clyde!
He hid it in the one place he knew he could hide something: his ass.
Five long years, he wore this watch up his ass. Then, when he died of
dysentery, he gave me the watch. Selina! Selina Kyle, you're fired! And
Bruce Wayne, why are you dressed up like Batman? I thought about you
every time I jerked off, dickhead. I don't know what you want, but I
know I can get it for you, with a minimum of fuss! Money, jewels, a
\emph{very} big ball of string.

\chapter{Introduction}\label{introduction}

Some go code \cite{placeholder}:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{var} \NormalTok{sem = }\FunctionTok{make}\NormalTok{(}\KeywordTok{chan} \DataTypeTok{int}\NormalTok{, MaxOutstanding)}

\KeywordTok{func} \NormalTok{handle(r *Request) \{}
    \DecValTok{1} \NormalTok{-> sem    }\CommentTok{// Wait for active queue to drain.}
    \NormalTok{process(r)  }\CommentTok{// May take a long time.}
    \NormalTok{<-sem       }\CommentTok{// Done; enable next request to run.}
\NormalTok{\}}

\KeywordTok{func} \NormalTok{Serve(queue }\KeywordTok{chan} \NormalTok{*Request) \{}
    \KeywordTok{for} \NormalTok{\{}
        \NormalTok{req := <-queue}
        \KeywordTok{go} \NormalTok{handle(req)  }\CommentTok{// Don't wait for handle to finish.}
    \NormalTok{\}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

Another example using Rust:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{use} \NormalTok{std::cell::RefCell;}
\KeywordTok{use} \NormalTok{std::fs::File;}
\KeywordTok{use} \NormalTok{std::path::Path;}
\KeywordTok{use} \NormalTok{std::rc::Rc;}

\KeywordTok{fn} \NormalTok{record_fps(last_time: &}\KeywordTok{mut} \DataTypeTok{f64}\NormalTok{, frames: &}\KeywordTok{mut} \DataTypeTok{usize}\NormalTok{) \{}
    \KeywordTok{if} \PreprocessorTok{cfg!}\NormalTok{(debug) \{}
        \KeywordTok{let} \NormalTok{now = time::precise_time_s();}
        \KeywordTok{if} \NormalTok{now >= *last_time + }\DecValTok{1}\NormalTok{f64 \{}
            \PreprocessorTok{println!}\NormalTok{(}\StringTok{"\{\} FPS"}\NormalTok{, *frames);}
            \NormalTok{*frames = }\DecValTok{0}\NormalTok{;}
            \NormalTok{*last_time = now;}
        \NormalTok{\} }\KeywordTok{else} \NormalTok{\{}
            \NormalTok{*frames += }\DecValTok{1}\NormalTok{;}
        \NormalTok{\}}
    \NormalTok{\}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\chapter{Results and Design}\label{results-and-design}

You're talking to me all wrong\ldots{} It's the wrong tone. You do it
again and I'll stab you in the face with a soldering iron. Hey, tell me,
does your mother sew? BOOM. Get her to sew that! This is my gun, Clyde!
You see, in this world there's two kinds of people, my friend: Those
with loaded guns and those who dig. You dig. don't p!ss down my back and
tell me it's raining. Did you hear about the happy Roman? He was ``glad
he ate her.'' What you have to ask yourself is, do I feel lucky. Well do
ya' punk? Well, do you have anything to say for yourself? I got a fever,
and the only prescription is more cowbell. Dyin' ain't much of a livin',
boy. This is America, babe, you gotta think big to be big. You got the
wrong guy, ace! What do you want me to say, that I'm sorry? That I
apologize? Well, people in Hell want ice water, pal.

\chapter{Background}\label{background}

Selina! Selina Kyle, you're fired! And Bruce Wayne, why are you dressed
up like Batman? When a naked man's chasing a woman through an alley with
a butcher knife and a hard-on, I figure he's not out collecting for the
Red Cross. Are you feeling lucky punk When a naked man's chasing a woman
through an alley with a butcher knife and a hard-on, I figure he's not
out collecting for the Red Cross. Did you hear about the happy Roman? He
was ``glad he ate her.'' You know why the Yankees always win, Frank?
it's 'cause the other teams can't stop staring at those damn pinstripes.
He hid it in the one place he knew he could hide something: his ass.
Five long years, he wore this watch up his ass. Then, when he died of
dysentery, he gave me the watch. You're talking to me all wrong\ldots{}
It's the wrong tone. You do it again and I'll stab you in the face with
a soldering iron. Hey, tell me, does your mother sew? BOOM. Get her to
sew that! I thought about you every time I jerked off, dickhead. Ever
notice how sometimes you come across somebody you shouldn't have F**ked
with? Well, I'm that guy. Are you feeling lucky punk Here. Put that in
your report!" AND ``I may have found a way out of here.

\chapter{Conclusion}\label{conclusion}

I'm neglecting my other guests. Enjoy yourself, you'll find the young
ladies stimulating company. Here. Put that in your report!" AND ``I may
have found a way out of here. What do you want me to say, that I'm
sorry? That I apologize? Well, people in Hell want ice water, pal. Man's
gotta know his limitations. You see, in this world there's two kinds of
people, my friend: Those with loaded guns and those who dig. You dig. I
don't know what you want, but I know I can get it for you, with a
minimum of fuss! Money, jewels, a \emph{very} big ball of string. This
is the AK-47 assault rifle, the preferred weapon of your enemy; and it
makes a distinctive sound when fired at you, so remember it. What you
have to ask yourself is, do I feel lucky. Well do ya' punk? You want a
guarantee, buy a toaster. You know why the Yankees always win, Frank?
it's 'cause the other teams can't stop staring at those damn pinstripes.
You got the wrong guy, ace! I got a fever, and the only prescription is
more cowbell.
